Non-word repetition in Yélî Dnye

### 2020-09-07 manuscript.tex
re-render table
some characters still mysteriously not showing up. grrrr.

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Non-word repetition in Yélî Dnye},
            pdfkeywords={phonology, non-word repetition, development},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{NWR in Yélî Dnye}
\author{Alejandrina Cristia\textsuperscript{1}\ \& Marisa Casillas\textsuperscript{2}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Laboratoire de Sciences Cognitives et de Psycholinguistique, Département d'Etudes cognitives, ENS, EHESS, CNRS, PSL University\\\textsuperscript{2} Max Planck Institute for Psycholinguistics}
\authornote{All data are made available in a repository in the Open Science Framework. AC acknowledges the support of the Agence Nationale de la Recherche (ANR-17-CE28-0007 LangAge, ANR-16-DATA-0004, ANR-14-CE30-0003, ANR-17-EURE-0017); and the J. S. McDonnell Foundation Understanding Human Cognition Scholar Award.

Correspondence concerning this article should be addressed to Alejandrina Cristia, 29, rue d’Ulm, 75005 Paris, France. E-mail: alecristia@gmail.com}
\keywords{phonology, non-word repetition, development\newline\indent Word count: ~xxx words}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  % load polyglossia as late as possible as it *could* call bidi if RTL lang (e.g. Hebrew or Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi

\title{Non-word repetition in Yélî Dnye}

\date{}

\abstract{
In nonword repetition (NWR) studies, participants are presented auditorily with an item that is phonologically legal but lexically meaningless in the local language. Accuracy is thought to reflect long-term phonological knowledge as well as online phonological working memory and flexible production patterns.In this study, we report on NWR results among children learning Yêly Dnyé, an isolate spoken in Rossel Island, PNG, with an unusually dense phonological inventory. This study contributes to three lines of research. First, we document that non-word items containing typologically rare sounds are repeated accurately less often that non-words containing more common sounds. Second, we document rather weak effects of item length, contributing to other research suggesting that length effects may be language-specific. Third, we do not find strong individual variation effects in this population, contrary to previous results documenting strong age-related effects. Together, these data provide a unique view of online phonological processing in a seldom-studied language, and contribute to both typological and language acquisition research.
}

@@

\hypertarget{todo-middy}{%
\subsection{TODO Middy}\label{todo-middy}}

@@

\hypertarget{todo-later}{%
\subsection{TODO later}\label{todo-later}}

\begin{itemize}
\tightlist
\item
  probably turn summary of types of error into a table; use proportion of correctly produced rather than number; use first attempts rather than the whole data set
\item
  maybe add to the last ana the prevalence (ie out of all the gh which proportion get transformed)
\item
  maybe add analyses of score as a function of frequency (phones, diphones) in MC's corpus? (mc suggested, but I don't think we need it\ldots{})
\end{itemize}

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

@@

\hypertarget{intro-to-the-language-mc---please-feel-free-to-throw-away-anything-that-is-not-useful}{%
\subsubsection{\texorpdfstring{Intro to the language (\textbf{mc}) - please feel free to throw away anything that is not useful!}{Intro to the language (mc) - please feel free to throw away anything that is not useful!}}\label{intro-to-the-language-mc---please-feel-free-to-throw-away-anything-that-is-not-useful}}

@@

\hypertarget{intro-to-the-people-mc---please-feel-free-to-throw-away-anything-that-is-not-useful}{%
\subsubsection{\texorpdfstring{Intro to the people (\textbf{mc}) - please feel free to throw away anything that is not useful!}{Intro to the people (mc) - please feel free to throw away anything that is not useful!}}\label{intro-to-the-people-mc---please-feel-free-to-throw-away-anything-that-is-not-useful}}

@@

\hypertarget{brief-review-of-nwr-for-our-purposes}{%
\subsubsection{Brief review of NWR for our purposes}\label{brief-review-of-nwr-for-our-purposes}}

@@

\hypertarget{research-questions}{%
\subsubsection{Research questions}\label{research-questions}}

@@

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\hypertarget{stimuli}{%
\subsubsection{Stimuli}\label{stimuli}}

@@

@@

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

@@

\hypertarget{coding}{%
\subsubsection{Coding}\label{coding}}

@@

\hypertarget{analyses}{%
\subsubsection{Analyses}\label{analyses}}

@@

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

\hypertarget{preliminary-analyses}{%
\subsubsection{Preliminary analyses}\label{preliminary-analyses}}

@@

\hypertarget{nwr-as-a-function-of-cross-linguistic-phone-frequency}{%
\subsubsection{NWR as a function of cross-linguistic phone frequency}\label{nwr-as-a-function-of-cross-linguistic-phone-frequency}}

@@

\hypertarget{accuracy-a-function-of-item-length}{%
\subsubsection{Accuracy a function of item length}\label{accuracy-a-function-of-item-length}}

@@

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:tablength}NWR scores measured in whole word accuracy, phoneme-based accuracy, and normalized Levenshtein Distance, separately for the four stimuli lengths.}

\begin{tabular}{lll}
\toprule
Word & \multicolumn{1}{c}{Phoneme} & \multicolumn{1}{c}{NLD}\\
\midrule
47 (22) & 59 (17) & 41 (17)\\
79 (22) & 94 (7) & 6 (7)\\
78 (19) & 94 (6) & 6 (6)\\
75 (32) & 93 (11) & 7 (11)\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

\hypertarget{factor-structuring-individual-variation}{%
\subsubsection{Factor structuring individual variation}\label{factor-structuring-individual-variation}}

@@

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

@@

\hypertarget{acknowledgments}{%
\subsection{Acknowledgments}\label{acknowledgments}}

We are grateful to informants and individuals who participated in the study. AC acknowledges financial and institutional support from Agence Nationale de la Recherche (ANR-17-CE28-0007 LangAge, ANR-16-DATA-0004 ACLEW, ANR-14-CE30-0003 MechELex, ANR-17-EURE-0017) and the J. S. McDonnell Foundation Understanding Human Cognition Scholar Award. MC blabla NWO Veni Innovational Scheme Grant (XXX-XX-XXX).

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-is08042009language}{}%
Action, C. (2009). Language impairment in a multilingual society: Linguistic patterns and the road to assessment. \emph{Brussels: COST Office. Available Online at: Http://Www. Bi-Sli. Org}.

\leavevmode\hypertarget{ref-balladares2016socio}{}%
Balladares, J., Marshall, C., \& Griffiths, Y. (2016). Socio-economic status affects sentence repetition, but not non-word repetition, in Chilean preschoolers. \emph{First Language}, \emph{36}(3), 338--351. \url{https://doi.org/10.1177/0142723715626067}

\leavevmode\hypertarget{ref-bowey2001nonword}{}%
Bowey, J. A. (2001). Nonword repetition and young children's receptive vocabulary: A longitudinal study. \emph{Applied Psycholinguistics}, \emph{22}(3), 441--469.

\leavevmode\hypertarget{ref-brandeker2015language}{}%
Brandeker, M., \& Thordardottir, E. (2015). Language exposure in bilingual toddlers: Performance on nonword repetition and lexical tasks. \emph{American Journal of Speech-Language Pathology}, \emph{24}(2), 126--138.

\leavevmode\hypertarget{ref-chiat2007preschool}{}%
Chiat, S., \& Roy, P. (2007). The preschool repetition test: An evaluation of performance in typically developing and clinically referred children. \emph{Journal of Speech, Language, and Hearing Research}, \emph{50}(2), 429--443.

\leavevmode\hypertarget{ref-cristia2020infant}{}%
Cristia, A., Farabolini, G., Scaff, C., Havron, N., \& Stieglitz, J. (2020). Infant-directed input and literacy effects on phonological processing: Non-word repetition scores among the tsimane'. \emph{Preprint}.

\leavevmode\hypertarget{ref-estes2007differences}{}%
Estes, K. G., Evans, J. L., \& Else-Quest, N. M. (2007). Differences in the nonword repetition performance of children with and without specific language impairment: A meta-analysis. \emph{Journal of Speech, Language, and Hearing Research}, \emph{50}(1), 177--195.

\leavevmode\hypertarget{ref-farmani2018normalization}{}%
Farmani, H., Sayyahi, F., Soleymani, Z., Labbaf, F. Z., Talebi, E., \& Shourvazi, Z. (2018). Normalization of the non-word repetition test in farsi-speaking children. \emph{Journal of Modern Rehabilitation}, \emph{12}(4), 217--224.

\leavevmode\hypertarget{ref-gallagher2014identity}{}%
Gallagher, G. (2014). An identity bias in phonotactics: Evidence from Cochabamba Quechua. \emph{Laboratory Phonology}, \emph{5}(3), 337--378. \url{https://doi.org/10.1515/lp-2014-0012}

\leavevmode\hypertarget{ref-gallon2007non}{}%
Gallon, N., Harris, J., \& Van der Lely, H. (2007). Non-word repetition: An investigation of phonological complexity in children with grammatical sli. \emph{Clinical Linguistics \& Phonetics}, \emph{21}(6), 435--455.

\leavevmode\hypertarget{ref-havron2019effect}{}%
Havron, N., Ramus, F., Heude, B., Forhan, A., Cristia, A., Peyre, H., \& Group, E. M.-C. C. S. (2019). The effect of older siblings on language development as a function of age difference and sex. \emph{Psychological Science}, \emph{30}(9), 1333--1343.

\leavevmode\hypertarget{ref-hazan2000development}{}%
Hazan, V., \& Barrett, S. (2000). The development of phonemic categorization in children aged 6--12. \emph{Journal of Phonetics}, \emph{28}(4), 377--396.

\leavevmode\hypertarget{ref-jabere2018xperiment}{}%
Jaber-Awida, A. (2018). Experiment in non word repetition by monolingual Arabic preschoolers. \emph{Athens Journal of Philology}, \emph{5}(4), 317--334. \url{https://doi.org/10.30958/ajp.5-4-4}

\leavevmode\hypertarget{ref-kalnak2014nonword}{}%
Kalnak, N., Peyrard-Janvid, M., Forssberg, H., \& Sahlén, B. (2014). Nonword repetition--a clinical marker for specific language impairment in swedish associated with parents' language-related problems. \emph{PloS One}, \emph{9}(2), e89544.

\leavevmode\hypertarget{ref-meir2017independent}{}%
Meir, N., \& Armon-Lotem, S. (2017). Independent and combined effects of socioeconomic status (ses) and bilingualism on children's vocabulary and verbal short-term memory. \emph{Frontiers in Psychology}, \emph{8}, 1442.

\leavevmode\hypertarget{ref-meir2016disentangling}{}%
Meir, N., Walters, J., \& Armon-Lotem, S. (2016). Disentangling sli and bilingualism using sentence repetition tasks: The impact of l1 and l2 properties. \emph{International Journal of Bilingualism}, \emph{20}(4), 421--452.

\leavevmode\hypertarget{ref-phoible}{}%
Moran, S., \& McCloy, D. (Eds.). (2019). \emph{PHOIBLE 2.0}. Jena: Max Planck Institute for the Science of Human History. Retrieved from \url{https://phoible.org/}

\leavevmode\hypertarget{ref-piazzalunga2019articulatory}{}%
Piazzalunga, S., Previtali, L., Pozzoli, R., Scarponi, L., \& Schindler, A. (2019). An articulatory-based disyllabic and trisyllabic non-word repetition test: Reliability and validity in italian 3-to 7-year-old children. \emph{Clinical Linguistics \& Phonetics}, \emph{33}(5), 437--456.

\leavevmode\hypertarget{ref-torrington2015non}{}%
Torrington Eaton, C., Newman, R. S., Ratner, N. B., \& Rowe, M. L. (2015). Non-word repetition in 2-year-olds: Replication of an adapted paradigm and a useful methodological extension. \emph{Clinical Linguistics \& Phonetics}, \emph{29}(7), 523--535.

\leavevmode\hypertarget{ref-vance2005speech}{}%
Vance, M., Stackhouse, J., \& Wells, B. (2005). Speech-production skills in children aged 3--7 years. \emph{International Journal of Language \& Communication Disorders}, \emph{40}(1), 29--48.

>>>>

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Non-word repetition in Yélî Dnye},
            pdfauthor={Alejandrina Cristia~\& Marisa Casillas},
            pdfkeywords={phonology, non-word repetition, development},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{NWR in Yélî Dnye}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Laboratoire de Sciences Cognitives et de Psycholinguistique, Département d'Etudes cognitives, ENS, EHESS, CNRS, PSL University\\\textsuperscript{2} Max Planck Institute for Psycholinguistics}
\keywords{phonology, non-word repetition, development\newline\indent Word count: ~xxx words}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\usepackage{lineno}

\linenumbers

\title{Non-word repetition in Yélî Dnye}
\author{Alejandrina Cristia\textsuperscript{1}~\& Marisa
Casillas\textsuperscript{2}}
\date{}

\authornote{All data are made available in a repository in the
Open Science Framework. AC acknowledges the support of the Agence
Nationale de la Recherche (ANR-17-CE28-0007 LangAge, ANR-16-DATA-0004,
ANR-14-CE30-0003, ANR-17-EURE-0017); and the J. S. McDonnell Foundation
Understanding Human Cognition Scholar Award.

Correspondence concerning this article should be addressed to
Alejandrina Cristia, 29, rue d'Ulm, 75005 Paris, France. E-mail:
\href{mailto:alecristia@gmail.com}{\nolinkurl{alecristia@gmail.com}}}

\abstract{
In nonword repetition (NWR) studies, participants are presented
auditorily with an item that is phonologically legal but lexically
meaningless in the local language. Accuracy is thought to reflect
long-term phonological knowledge as well as online phonological working
memory and flexible production patterns.In this study, we report on NWR
results among children learning Yêly Dnyé, an isolate spoken in Rossel
Island, PNG, with an unusually dense phonological inventory. This study
contributes to three lines of research. First, we document that non-word
items containing typologically rare sounds are repeated accurately less
often that non-words containing more common sounds. Second, we document
rather weak effects of item length, contributing to other research
suggesting that length effects may be language-specific. Third, we do
not find strong individual variation effects in this population,
contrary to previous results documenting strong age-related effects.
Together, these data provide a unique view of online phonological
processing in a seldom-studied language, and contribute to both
typological and language acquisition research.

}

@@

\subsection{TODO Middy}\label{todo-middy}

@@

\subsection{TODO later}\label{todo-later}

\begin{itemize}
\tightlist
\item
  probably turn summary of types of error into a table; use proportion
  of correctly produced rather than number; use first attempts rather
  than the whole data set DONE
\item
  maybe add to the last ana the prevalence (ie out of all the gh which
  proportion get transformed) DONE I think\ldots{} (this item looks the
  same as one of the three above)
\item
  maybe add analyses of score as a function of frequency (phones,
  diphones) in MC's corpus? (mc suggested, but I don't think we need
  it\ldots{}) - waiting until we talk about this
\end{itemize}

\subsection{Introduction}\label{introduction}

@@

\subsubsection{\texorpdfstring{Intro to the language (\textbf{mc}) -
please feel free to throw away anything that is not
useful!}{Intro to the language (mc) - please feel free to throw away anything that is not useful!}}\label{intro-to-the-language-mc---please-feel-free-to-throw-away-anything-that-is-not-useful}

@@

\subsubsection{\texorpdfstring{Intro to the people (\textbf{mc}) -
please feel free to throw away anything that is not
useful!}{Intro to the people (mc) - please feel free to throw away anything that is not useful!}}\label{intro-to-the-people-mc---please-feel-free-to-throw-away-anything-that-is-not-useful}

@@

\subsubsection{Brief review of NWR for our
purposes}\label{brief-review-of-nwr-for-our-purposes}

@@

\subsubsection{Research questions}\label{research-questions}

@@

\subsection{Methods}\label{methods}

\subsubsection{Stimuli}\label{stimuli}

@@

\begin{table}

\caption{\label{tab:tab2-stims}NWR stimuli in orthographic and phonological representations.}
\centering
\begin{tabular}[t]{llllllllll}
\toprule
\multicolumn{2}{c}{Practice} & \multicolumn{2}{c}{Monosyll} & \multicolumn{2}{c}{Bisyll} & \multicolumn{2}{c}{Trisyll} & \multicolumn{2}{c}{Tetrasyll} \\
\cmidrule(l{3pt}r{3pt}){1-2} \cmidrule(l{3pt}r{3pt}){3-4} \cmidrule(l{3pt}r{3pt}){5-6} \cmidrule(l{3pt}r{3pt}){7-8} \cmidrule(l{3pt}r{3pt}){9-10}
Orth. & Phon. & Orth. & Phon. & Orth. & Phon. & Orth. & Phon. & Orth. & Phon.\\
\midrule
nopimade & ṇɔpimædɛ & dp:a & ṭpæ͂ & kamo & kæmɔ & dimope & ṭimɔpɛ & diponate & ṭipɔṇætɛ\\
poni & pɔṇi & dpa & ṭpæ & kani & kæṇi & diyeto & ṭijɛtɔ & nomiwake & ṇɔmiwækɛ\\
wî & wɯ & dpâ & ṭpɑ & kipo & kipɔ & meyadi & mɛjæṭi & todiwuma & tɔṭiwumæ\\
 &  & dpê & ṭpə & noki & ṇɔki & mituye & mitujɛ & wadikeno & wæṭikɛṇɔ\\
 &  & dpéé & ṭpe: & nomi & ṇɔmi & nademo & ṇædɛmɔ &  & \\
\addlinespace
 &  & dpi & ṭpi & piwa & piwæ & nayeki & ṇæjɛki &  & \\
 &  & dpu & ṭpu & towi & tɔwi & nuyedi & ṇujɛdi &  & \\
 &  & gh:ââ & ɣɑ: & tupa & tupæ & pedumi & pɛdumi &  & \\
 &  & ghuu & ɣu: &  &  & tiwune & tiwuṇɛ &  & \\
 &  & kp:ââ & kpɑ͂: &  &  & tumowe & tumɔwɛ &  & \\
\addlinespace
 &  & kpu & kpu &  &  & widone & wiṭɔṇɛ &  & \\
 &  & lv:ê & lβʲə &  &  & wumipo & wumipɔ &  & \\
 &  & lva & lβʲæ &  &  &  &  &  & \\
 &  & lvi & lβʲi &  &  &  &  &  & \\
 &  & t:êê & tə͂ː &  &  &  &  &  & \\
\addlinespace
 &  & tp:a & tpæ͂ &  &  &  &  &  & \\
 &  & tpâ & tpɑ &  &  &  &  &  & \\
 &  & tpê & tpə &  &  &  &  &  & \\
\bottomrule
\end{tabular}
\end{table}

@@

\subsubsection{Procedure}\label{procedure}

@@

\subsubsection{Coding}\label{coding}

@@

\subsubsection{Analyses}\label{analyses}

@@

\subsubsection{Participants}\label{participants}

@@

\subsection{Results}\label{results}

\subsubsection{Preliminary analyses}\label{preliminary-analyses}

@@

\subsubsection{NWR as a function of cross-linguistic phone
frequency}\label{nwr-as-a-function-of-cross-linguistic-phone-frequency}

@@

\subsubsection{Accuracy a function of item
length}\label{accuracy-a-function-of-item-length}

@@

\begin{verbatim}
## 
## 
## \begin{table}[tbp]
## \begin{center}
## \begin{threeparttable}
## \caption{\label{tab:tablength}NWR scores measured in whole word accuracy, phoneme-based accuracy, and normalized Levenshtein Distance, separately for the four stimuli lengths.}
## \begin{tabular}{lll}
## \toprule
## Word & \multicolumn{1}{c}{Phoneme} & \multicolumn{1}{c}{NLD}\\
## \midrule
## 47 (22) & 59 (17) & 41 (17)\\
## 79 (22) & 94 (7) & 6 (7)\\
## 78 (19) & 94 (6) & 6 (6)\\
## 75 (32) & 93 (11) & 7 (11)\\
## \bottomrule
## \end{tabular}
## \end{threeparttable}
## \end{center}
## \end{table}
\end{verbatim}

\subsubsection{Factor structuring individual
variation}\label{factor-structuring-individual-variation}

@@

\subsection{Discussion}\label{discussion}

@@

\subsection{Acknowledgments}\label{acknowledgments}

We are grateful to the individuals who participated in the study. The
collection and annotation of these recordings was made possible by
Ndapw:éé Yidika, Taakêmê Ńamono, and Y:aaw:aa Pikuwa; with thanks also
to the PNG National Research Institute, and the Administration of Milne
Bay Province AC acknowledges financial and institutional support from
Agence Nationale de la Recherche (ANR-17-CE28-0007 LangAge,
ANR-16-DATA-0004 ACLEW, ANR-14-CE30-0003 MechELex, ANR-17-EURE-0017) and
the J. S. McDonnell Foundation Understanding Human Cognition Scholar
Award. MC acknowledges financial support from an NWO Veni Innovational
Scheme grant (275-89-033).

\section{References}\label{references}

@@

\hypertarget{refs}{}
\hypertarget{ref-is08042009language}{}
Action, C. (2009). Language impairment in a multilingual society:
Linguistic patterns and the road to assessment. \emph{Brussels: COST
Office. Available Online at: Http://Www. Bi-Sli. Org}.

\hypertarget{ref-balladares2016socio}{}
Balladares, J., Marshall, C., \& Griffiths, Y. (2016). Socio-economic
status affects sentence repetition, but not non-word repetition, in
Chilean preschoolers. \emph{First Language}, \emph{36}(3), 338--351.
doi:\href{https://doi.org/10.1177/0142723715626067}{10.1177/0142723715626067}

\hypertarget{ref-bowey2001nonword}{}
Bowey, J. A. (2001). Nonword repetition and young children's receptive
vocabulary: A longitudinal study. \emph{Applied Psycholinguistics},
\emph{22}(3), 441--469.

\hypertarget{ref-brandeker2015language}{}
Brandeker, M., \& Thordardottir, E. (2015). Language exposure in
bilingual toddlers: Performance on nonword repetition and lexical tasks.
\emph{American Journal of Speech-Language Pathology}, \emph{24}(2),
126--138.

\hypertarget{ref-chiat2007preschool}{}
Chiat, S., \& Roy, P. (2007). The preschool repetition test: An
evaluation of performance in typically developing and clinically
referred children. \emph{Journal of Speech, Language, and Hearing
Research}, \emph{50}(2), 429--443.

\hypertarget{ref-cristia2020infant}{}
Cristia, A., Farabolini, G., Scaff, C., Havron, N., \& Stieglitz, J.
(2020). Infant-directed input and literacy effects on phonological
processing: Non-word repetition scores among the tsimane'.
\emph{Preprint}.

\hypertarget{ref-estes2007differences}{}
Estes, K. G., Evans, J. L., \& Else-Quest, N. M. (2007). Differences in
the nonword repetition performance of children with and without specific
language impairment: A meta-analysis. \emph{Journal of Speech, Language,
and Hearing Research}, \emph{50}(1), 177--195.

\hypertarget{ref-farmani2018normalization}{}
Farmani, H., Sayyahi, F., Soleymani, Z., Labbaf, F. Z., Talebi, E., \&
Shourvazi, Z. (2018). Normalization of the non-word repetition test in
farsi-speaking children. \emph{Journal of Modern Rehabilitation},
\emph{12}(4), 217--224.

\hypertarget{ref-gallagher2014identity}{}
Gallagher, G. (2014). An identity bias in phonotactics: Evidence from
Cochabamba Quechua. \emph{Laboratory Phonology}, \emph{5}(3), 337--378.
doi:\href{https://doi.org/10.1515/lp-2014-0012}{10.1515/lp-2014-0012}

\hypertarget{ref-gallon2007non}{}
Gallon, N., Harris, J., \& Van der Lely, H. (2007). Non-word repetition:
An investigation of phonological complexity in children with grammatical
sli. \emph{Clinical Linguistics \& Phonetics}, \emph{21}(6), 435--455.

\hypertarget{ref-havron2019effect}{}
Havron, N., Ramus, F., Heude, B., Forhan, A., Cristia, A., Peyre, H., \&
Group, E. M.-C. C. S. (2019). The effect of older siblings on language
development as a function of age difference and sex. \emph{Psychological
Science}, \emph{30}(9), 1333--1343.

\hypertarget{ref-hazan2000development}{}
Hazan, V., \& Barrett, S. (2000). The development of phonemic
categorization in children aged 6--12. \emph{Journal of Phonetics},
\emph{28}(4), 377--396.

\hypertarget{ref-jabere2018xperiment}{}
Jaber-Awida, A. (2018). Experiment in non word repetition by monolingual
Arabic preschoolers. \emph{Athens Journal of Philology}, \emph{5}(4),
317--334.
doi:\href{https://doi.org/10.30958/ajp.5-4-4}{10.30958/ajp.5-4-4}

\hypertarget{ref-kalnak2014nonword}{}
Kalnak, N., Peyrard-Janvid, M., Forssberg, H., \& Sahlén, B. (2014).
Nonword repetition--a clinical marker for specific language impairment
in swedish associated with parents' language-related problems.
\emph{PloS One}, \emph{9}(2), e89544.

\hypertarget{ref-meir2017independent}{}
Meir, N., \& Armon-Lotem, S. (2017). Independent and combined effects of
socioeconomic status (ses) and bilingualism on children's vocabulary and
verbal short-term memory. \emph{Frontiers in Psychology}, \emph{8},
1442.

\hypertarget{ref-meir2016disentangling}{}
Meir, N., Walters, J., \& Armon-Lotem, S. (2016). Disentangling sli and
bilingualism using sentence repetition tasks: The impact of l1 and l2
properties. \emph{International Journal of Bilingualism}, \emph{20}(4),
421--452.

\hypertarget{ref-phoible}{}
Moran, S., \& McCloy, D. (Eds.). (2019). \emph{PHOIBLE 2.0}. Jena: Max
Planck Institute for the Science of Human History. Retrieved from
\url{https://phoible.org/}

\hypertarget{ref-piazzalunga2019articulatory}{}
Piazzalunga, S., Previtali, L., Pozzoli, R., Scarponi, L., \& Schindler,
A. (2019). An articulatory-based disyllabic and trisyllabic non-word
repetition test: Reliability and validity in italian 3-to 7-year-old
children. \emph{Clinical Linguistics \& Phonetics}, \emph{33}(5),
437--456.

\hypertarget{ref-torrington2015non}{}
Torrington Eaton, C., Newman, R. S., Ratner, N. B., \& Rowe, M. L.
(2015). Non-word repetition in 2-year-olds: Replication of an adapted
paradigm and a useful methodological extension. \emph{Clinical
Linguistics \& Phonetics}, \emph{29}(7), 523--535.

\hypertarget{ref-vance2005speech}{}
Vance, M., Stackhouse, J., \& Wells, B. (2005). Speech-production skills
in children aged 3--7 years. \emph{International Journal of Language \&
Communication Disorders}, \emph{40}(1), 29--48.

\hypertarget{ref-wilsenach2013phonological}{}
Wilsenach, C. (2013). Phonological skills as predictor of reading
success: An investigation of emergent bilingual Northern Sotho/English
learners. \emph{Per Linguam: a Journal of Language Learning= Per
Linguam: Tydskrif vir Taalaanleer}, \emph{29}(2), 17--32.
doi:\href{https://doi.org/10.5785/29-2-554}{10.5785/29-2-554}

\hypertarget{ref-is08042009language}{}
Action, C. (2009). Language impairment in a multilingual society:
Linguistic patterns and the road to assessment. \emph{Brussels: COST
Office. Available Online at: Http://Www. Bi-Sli. Org}.
